Should I Airbnb My Property?

### 2017-02-17 abb_Writeup.Rmd
dc prop and list  type review

Here we describe the operations that we have performed to prepare the two sets of raw data for analysis.  Primarily, this involves the filtering out data errors, outlier values and other observations than contain data that do not fit our research questions. Additionally, as our data are from two different sources, a number of fields also require standardization so that comparisons between the two leasing strategy options  -- long-term rental (LTR) vs short-term rental (STR) -- can be made.

@@

```{r load_beforePT, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide'}
  data.path <- 'c:/dropbox/research/airBNB/data/'
  load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
```

<!-- ```{r type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'} -->

<!--   # Create Airbnb plot -->

<!--   abb.types <- ggplot(abb.data1, aes(x=type)) + -->
<!--     geom_bar(color=str.col, fill=str.col) + -->
<!--     xlab('') + -->
<!--     ylab('# of Properties\n') + -->
<!--     labs(title = "Short Term Rentals\n") + -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--   # Create long term rental plot -->

<!--   ltr.types <- ggplot(ltr.data1, aes(x=type)) + -->
<!--     geom_bar(color=ltr.col, fill=ltr.col) + -->
<!--     xlab('') + -->
<!--     ylab('# of Properties\n') + -->
<!--     labs(title = "Long Term Rentals\n") + -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--   # Output plots -->

<!--   ggMultiPlots(abb.types, ltr.types, cols=2) -->

<!-- ```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->

<!--   abb.data1 <- subset(abb.data1, type != 'Other') -->
<!--   ltr.data1 <- subset(ltr.data1, type != 'Other') -->

<!-- Next, the short-term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked: -->

<!-- 1. **Entire Home/Apt**: The entire home or apartment is available -->
<!-- 2. **Private Room**: One room within a house or apartment is available -->
<!-- 3. **Shared Room**: A bed within a room shared by another occupant(s) is available -->

<!-- As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment. Unfortunately, this filter does remove about 40% of the short-term data (Figure 2), however, given the research question it is unavoidable. -->

<!-- ```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals'} -->

<!--   # Fix data types and names -->

<!--   abb.data1$listing.type <- as.character(abb.data1$listing.type) -->
<!--   abb.data1$listing.type[abb.data1$listing.type == 'Entire home/apt'] <- 'Entire home' -->

<!--   # Make Plot -->

<!--   ggplot(abb.data1, aes(x=listing.type)) + -->
<!--     geom_bar(color=abb.col[1], fill=abb.col[1]) + -->
<!--     xlab('') + -->
<!--     ylab('# of Properties\n') + -->
<!--     labs(title = "Short Term Rentals \nby Listing Type\n") + -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!-- ```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE} -->

<!--   abb.data1 <- abb.data1[abb.data1$listing.type == 'Entire home', ] -->

>>>>

Here we describe the operations that we have performed to prepare the two sets of raw data for analysis. Primarily, this involves the filtering out data errors, outlier values and other observations than contain data that do not fit our research questions. Additionally, as our data are from two different sources, a number of fields require standardization so that comparisons between the two leasing strategy options -- long-term rental (LTR) vs short-term rental (STR) -- can be made.

@@

```{r load_beforePT, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}
  data.path <- 'c:/dropbox/research/airBNB/data/'
  load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
```

```{r load_ptplot, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'}

  load(paste0(fig.path, 'ltrtypes.RData'))
  load(paste0(fig.path, 'strtypes.RData'))

  ggMultiPlots(str.types, ltr.types, cols=2)

Next, the short-term rentals properties can be listed as one of three types relating to the extent of the property which is able to be booked:

1. **Entire Home/Apt**: The entire home or apartment is available
2. **Private Room**: One room within a house or apartment is available
3. **Shared Room**: A bed within a room shared by another occupant(s) is available

As long-term rentals do not offer **Private Room** or **Shared Room** options^[Our dataset does not include rooming houses, purpose built student accommodations and other types of rentals which may offer private or shared room options] and our purpose here is a comparison of long- and short-term returns, we remove all short-term properties that do not lease the entire home or apartment. Unfortunately, this filter does remove about 40% of the short-term data (Figure 2), however, given the research question it is unavoidable.

```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals'}

 load(paste0(fig.path, 'listtypes.RData'))

 list.types
